Modelling the emergence of whisker barrels

### 2020-06-16 paper/briefpaper/brief.tex
Reruns the stats for my now correct version of eta and updates the paper accordingly.

\cmnt{First, we conducted 10 runs of the simulation shown in
  Fig.\,\ref{fig:main}C to evaluate the mean and standard deviation of the
  three metrics in the default model. The
  results (where deviations occur as a result of the different random initial
  conditions for $a_i$) were $\delta=0.089\,(0.004)$, $\eta=113.5\textbf{!!}\,(1.2)$ and
  $\omega=0.2165\,(0.0001)$. None of the three metrics were strongly affected
  by the random changes to $a_i$ on each run. The results give a baseline from
  which to evaluate whether changes in the other inputs have a statistically
  significant effect.}

\cmnt{Next, we modified the parameters of the generating uniform distribution
  to initialize $a_i$ for each hex to $0.1+{U}(0,0.4)$ (increasing the variability of
  $a_i(\mb{x},t=0)$ without changing the mean initial activation). We ran this
  system 10 times and obtained the results $\delta=0.090\,(0.005)$,
  $\eta=115\,(1.9)\textbf{!!}$ and $\omega=0.2166\,(0.0003)$. Paired two-sample t-tests
  demonstrated that the increase in noise amplitude made no significant
  difference to the metric results ($\delta:
  \mathrm{t}=-0.69,\mathrm{p}=0.49$,
  $\eta: \mathrm{t}=-2.0,\mathrm{p}=0.06\textbf{!!}$,
  $\omega: \mathrm{t}=-1.7,\mathrm{p}=0.11$). 10 runs of a
  noise-free initial condition with $a_i=0.3$ for every hex showed that
  the model is deterministic (all runs produced the results $\delta=0.0928$,
  $\eta=114.31\textbf{!!}$ and $\omega=0.21649$) and that stochasticity in
  $a_i(\mb{x},t=0)$ is not required by this model, as all three results lay within
  one standard deviation of those for the runs in which $a_i$ was initialized stochastically.}

>>>>

\cmnt{First, we conducted 10 runs of the simulation shown in
  Fig.\,\ref{fig:main}C to evaluate the mean and standard deviation of the
  three metrics in the default model. The
  results (where deviations occur as a result of the different random initial
  conditions for $a_i$) were $\delta=0.089\,(0.004)$, $\eta=0.2108\,(0.002)$ and
  $\omega=0.2165\,(0.0001)$. None of the three metrics were strongly affected
  by the random changes to $a_i$ on each run. The results give a baseline from
  which to evaluate whether changes in the other inputs have a statistically
  significant effect.}

\cmnt{Next, we modified the parameters of the generating uniform distribution
  to initialize $a_i$ for each hex to $0.1+{U}(0,0.4)$ (increasing the variability of
  $a_i(\mb{x},t=0)$ without changing the mean initial activation). We ran this
  system 10 times and obtained the results $\delta=0.090\,(0.005)$,
  $\eta=0.2136\,(0.004)$ and $\omega=0.2166\,(0.0003)$. Paired two-sample t-tests
  demonstrated that the increase in noise amplitude made no significant
  difference to the metric results ($\delta:
  \mathrm{t}=-0.69,\mathrm{p}=0.49$,
  $\eta: \mathrm{t}=-2.0,\mathrm{p}=0.06$,
  $\omega: \mathrm{t}=-1.7,\mathrm{p}=0.11$). 10 runs of a
  noise-free initial condition with $a_i=0.3$ for every hex showed that
  the model is deterministic (all runs produced the results $\delta=0.0928$,
  $\eta=0.21236$ and $\omega=0.21649$) and that stochasticity in
  $a_i(\mb{x},t=0)$ is not required by this model, as all three results lay within
  one standard deviation of those for the runs in which $a_i$ was initialized stochastically.}
